### 2018-04-28 paper/algorithm.tex
Writes up algorithm section, merges relevant parts of Adrien's old stuff

% \NewCryptoEntity{\Alice}{A}
% \NewCryptoEntity{\Bob}{B}
% \NewCryptoEntity{\Carol}{C}
% % Arg, already used \mathcal{D} for the devices set
% \NewCryptoEntity{\David}{D}

\newcommand{\Alice}{\ensuremath{\mathscr{A}}}
\newcommand{\Bob}{\ensuremath{\mathscr{B}}}

\newcommand{\localoverlay}{Squad Overlay\xspace}
\newcommand{\globaloverlay}{Global Overlay\xspace}

@@

\subsection{Predictions and scheduling}

\commentDaniel{%
  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used above 
  (\cref{ExtendRoute}).%
}

@@

\commentDaniel{%
  Anything below this line should be updated, integrated or removed.%
}
A set of users $\mathcal{U}$ participate in the \name network.
Each user $u \in \mathcal{U}$ has a set $\mathcal{D}_u$ of devices that contribute to the system when online.
Alice and Bob use \name to exchange a file secretly: no participant will learn who sends and receives it, nor its content.

On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
We call this part of the protocol the \localoverlay, and present it in 
\cref{local-overlay}. On the other hand, user's collectively upload the list of 
their connected devices and associated future predictions to a Distributed Hash 
Table (DHT): it serves as a registry of online peers (including connection 
probabilities for the next turn), and for the routing of files.
We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
two users is enabled by the two previous protocols, and is covered in 
\cref{file-exchange}

Each device initially only knows when it is connected. 
To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
To do so, they employ a probabilistic dissemination protocol, based on previous work from our team~\cite{luxey:hal-01704172}.
This algorithm, called \textsc{Sprinkler}, allows devices to gossip any new connection information to random peers, ensuring that all devices know the full observation sequence with a very high probability.
\textsc{Sprinkler} has shown resilient to devices churn~\cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.

% All swarms participate in the Inter-Swarm Protocol to coordinate the global 
% knowledge needed by the swarms to interact.
% More specifically, the global knowledge contains:
% \begin{itemize}
%   \item A table, \(R\), of devices available for routing;
%   \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
%     fixed-length strings of length \(\lambda\) to arbitrary-length strings.
% \end{itemize}

Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
\begin{enumerate}
  \item Providing routing information to nodes during file exchange. This is 
    discussed in-depth in \cref{file-exchange};
	\item Listing online devices and their probability of being online next time step.
\end{enumerate}

Every time a device is online, it sends the following information to the DHT:
\begin{itemize}
	\item the time \commentAL{step?};
	\item its address;
	\item its public key;
	\item the probability that it will still be connected next turn \commentAL{no interest in t+2 and more.}
\end{itemize}

\commentAL{Cite DHT articles and emphasize their security guarantees.}

We consider two users, Alice and Bob, such that Alice wants to send a file to Bob secretly.
They want to keep the file content secret to anybody but them; \name's users should not know who sent a file to whom; and Alice and Bob want to hide their address from one another.

In other words, \name must guarantee \emph{sender-receiver anonymity}.
To achieve this, communications go through onion routes, using rendez-vous points.
Our approach is tightly based on the Tor seminal paper~\cite{Tor}.

The device that contains Alice's file \commentAL{I don't like that dependence on the file's location} creates routes to several Introductory Points (IP), chosen at random among connected peers.
Alice uploads the addresses of her IP to the DHT at the position $k$.
One of Bob's devices creates routes to several Rendez-Vous points (RV), randomly picked among peers that will be connected in the next time step.
Bob fetches the addresses of Alice's IP from the \ac{DHT}.
Then, he sends a packet containing the addresses of its chosen RV to Alice's IPs.
The IP nodes forward the packet to Alice's device. 
Alice chunks her file into pieces of a predefined size, encrypted using $ek$.

Starting from the next round, Alice will send all chunks of her file to Bob's RV, that will forward it to Bob.
Once the file is received, everybody is happy and all routes are killed.

% subsubsection file_exchange_process (end)

\subsubsection{Onion routes in face of churn}% (fold)
\label{ssub:onion_routes_in_face_of_churn}

An onion route between A and B consists of several servers (usually three) that serve as relays, say $r_1, r_2$ and $r_3$. 
The route will have a fixed order: $A \rightarrow r_1 \rightarrow r_2 \rightarrow r_3 \rightarrow B$.
Every time data travels through the onion route, it is encrypted---along with its header---with symmetric keys, such that no-one except the sender and the receiver can read its content.
A node only knows its direct predecessor (that sent the packet) and its direct successor (whose address is the only one readable by it) on the route, such that only the creator of the route (A) knows the destination (B).

Alas, when one node goes down along the way, the route has to be recreated, at least partly.
Alice will be informed of the crash by the predecessor of the failed node with a control message, using the onion route.
Then, she will have to select a new connected peer, and ask the predecessor of the failed node to re-establish the route using this new peer.
This is fine in scenarii where participating servers only fail sporadically.
But in our setup, where devices disconnection is a certainty, we need a more robust approach.

We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be 
the \emph{set} of possibly disconnected devices that will take the 
$i^{\text{th}}$ position in our onion route.
In traditional onion routing, $r_1$ is the only one knowing the address of $r_2$, because it is written encrypted with its public key in the header.
Here, every device in the $R_i$ can read the set $R_{i+1}$ in the header, because the symmetric key $sk$ used to encrypt the set $R_{i+1}$ is known to every device in $R_i$.
The header indeed contains a version of $sk$ for each device $r_{i,j}$, encrypted with its own public key $pk_{r_{i,j}}$.

In the following equation, $S(sk,\texttt{message})$ means that $\texttt{message}$ is encrypted with the symmetric key $sk$, while $P(pk, \texttt{message})$ means that $\texttt{message}$ is encrypted using the public key $pk$.
Follows the content of the header in our version of the onion routing, considering that $R_i=\{r_{i,1}, r_{i,2}, r_{i,3}\}$, that $pk_{r_{i,j}}$ is $r_{i,j}$'s public key, and that $||$ means concatenation:
\[
  P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, 
  R_{i+1})
\]

(I read that this is how PGP handles multiple recipients.)

>>>>

Alice and Bob each has a set of devices containing their files, \eg a 
smartphone, laptop and a desktop computer.
Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
share a file, \(f\), with Bob.
Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
desktop computer.
She gives some metadata about \(f\) to Bob, at least the file size.
Bob creates an onion route of low-availability devices with some subset of Bob's 
devices as the destination.
The layers of the route are chosen such that the probability of all devices 
being offline at the same time is low.
Bob gives this route to Alice.
Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
gets the route and the instruction to send \(f\) using this route.
When Alice's desktop computer receives this instruction it will create the first 
half of the route and concatenate it with Bob's route, then transfer \(f\) to 
Bob.
In this section we will present the details of the necessary algorithms.

We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
\(D_u\).
We call \(D_u\) the device swarm of \(u\).
Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
swarm, \(D_b\).
We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
swarm.

Without loss of generality, we will use Alice and Bob as examples.
Each of Alice's (and Bob's) devices will keep track of its own online and 
offline behaviour.
They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
each other's online--offline behaviour.
\commentDaniel{Is that correct?}
This allows Alice's device swarm to do internal scheduling.

Each device \(d\in D_a\) will also participate in the global device swarm, 
\(D\supset D_a\).

\newcommand{\localoverlay}{Local Overlay\xspace}
\newcommand{\globaloverlay}{Global Overlay\xspace}

Each device initially only knows when it is connected. 
To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
To do so, they employ a probabilistic dissemination protocol, 
\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
This allows devices to gossip any new connection information to random peers in 
the local swarm, ensuring that all devices know the full observation sequence 
with a very high probability.
\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
is thus perfectly suited for our purpose, where a user's devices often 
disconnect and reconnect.

Every time a device is online, it participates in the random peer sampling 
protocol.
If a device is sampled it provides the following information:
\begin{itemize}
  \item its address;
	\item its public key;
  \item the probability of being online.
\end{itemize}

\subsection{Random peer sampling and predictions}

\commentDaniel{%
  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
  \cref{ExtendRoute}.
  This is probably part of getting random peers in the same place.%
}

\commentDaniel{%
  What is the probability distribution of the peer sample that we get?
  Will it be close to uniformly random?%
}

@@

\subsection{Scheduling a file transfer}

@@

\endinput
